The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-06-14 article.tex
Describe RNG seed selectiion better

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description & Values \\
    \hline
    \hline
    $b_g$                 & Speciation initiation rate of a good species & 0.3, 0.5 \\
    $b_i$                 & Speciation initiation rate of an incipient species & 0.3, 0.5 \\
    $\lambda$             & Speciation completion rate & 0.1, 0.3, 1.0, $\infty$ \\
    $\mu_g$               & Extinction rate of a good species & 0.0, 0.1, 0.2 \\
    $\mu_i$               & Extinction rate of an incipient species & 0.0, 0.1, 0.2 \\
    \hline
    $t_c$                 & Crown age & 15 \\
    $\sigma_c$            & Standard deviation around crown age & 0.001 \\
    $M_s$                 & Sampling method & S, L, R \\
    $M_c$                 & Clock model & S, RLN \\
    $M_t$                 & Site model & JC69, GTR \\
    $r$                   & Mutation rate & $\frac{1}{15}$ \\
    $l_a$                 & DNA alignment length & $15K$ \\
    $f_i$                 & MCMC sampling interval & 1K or more \\
    $R_i$                 & RNG seed incipient tree and randomly sampled species tree & 1, 2, ... \\
    $R_a$                 & RNG seed alignment simulation & $R_i$ \\
    $R_b$                 & RNG seed BEAST2 & $R_i$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. Above the horizontal line is 
    the biological parameter set. 
    The RNG seed $R_i$ is 1 for the first simulation of the general data set, 2 for the next,
    and so on, up to and including 3480. The RNG seeds for the data set investigating the effect 
    of sampling continues from there.
    The sampling methods are abbreviated as such: 'R' denotes random
    sampling, 'S' is 'shortest' and 'L' is 'longest'. Sampling method $M_s$ is random for the general
    data set. For the data set exploring the effect of sampling, we use 'shortest'
    for odd values of $R_i$, and 'longest' for even values of $R_i$.
    The clock models are abbreviated as 'S' for a strict and 'RLN' for a relaxed log-normal model.
    The site models are abbreviated as 'JC69' for Jukes-Cantor (\cite{jc69}) and 'GTR' for the generalized 
    time-reversible model (\cite{gtr}).
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \centering 
  \begin{tabular}{p{0.05\textwidth} p{0.6\textwidth} p{0.2\textwidth}}
    \hline
                          & Description & Values \\
    \hline
    \hline
    $b_g$                 & Speciation initiation rate of a good species & 0.3, 0.5 \\
    $b_i$                 & Speciation initiation rate of an incipient species & 0.3, 0.5 \\
    $\lambda$             & Speciation completion rate & 0.1, 0.3, 1.0, $\infty$ \\
    $\mu_g$               & Extinction rate of a good species & 0.0, 0.1, 0.2 \\
    $\mu_i$               & Extinction rate of an incipient species & 0.0, 0.1, 0.2 \\
    \hline
    $t_c$                 & Crown age & 15 \\
    $\sigma_c$            & Standard deviation around crown age & 0.001 \\
    $M_s$                 & Sampling method & S, L, R \\
    $M_c$                 & Clock model & S, RLN \\
    $M_t$                 & Site model & JC69, GTR \\
    $r$                   & Mutation rate & $\frac{1}{15}$ \\
    $l_a$                 & DNA alignment length & $15K$ \\
    $f_i$                 & MCMC sampling interval & 1K or more \\
    $R_i$                 & RNG seed incipient tree and randomly sampled species tree & 1, 2, ... \\
    $R_a$                 & RNG seed alignment simulation & $R_i$ \\
    $R_b$                 & RNG seed BEAST2 & $R_i$ \\
    \hline
  \end{tabular}
  \caption{
    Overview of the simulation parameters. Above the horizontal line is 
    the biological parameter set. 
    The RNG seed $R_i$ is 1 for the first simulation of the general data set, 2 for the next,
    and so on, up to and including 3480. The RNG seeds for the data set investigating the effect 
    of sampling continue from there, but only those RNG seeds are used in which sampling has an effect.
    The sampling methods are abbreviated as such: 'R' denotes random
    sampling, 'S' is 'shortest' and 'L' is 'longest'. Sampling method $M_s$ is random for the general
    data set. For the data set exploring the effect of sampling, we use 'shortest'
    and 'longest' for each value of $R_i$ (which are random seeds in which sampling has an effect).
    The clock models are abbreviated as 'S' for a strict and 'RLN' for a relaxed log-normal model.
    The site models are abbreviated as 'JC69' for Jukes-Cantor (\cite{jc69}) and 'GTR' for the generalized 
    time-reversible model (\cite{gtr}).
  }
  \label{table:parameters}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
